---
title: "linear model from Web"
author: "Sarah Castellon"
date: "October 3 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
model.1=lm(SIMS~ARM, data=data)
abline(model.1)
```  

This scatter plot reflects simulated strength (SIMS) increases as ARM strength increased.     

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
.69 reflects a moderate positive correlation between SIMS and ARM strength.

### Inferential  (Build model.1)

```{r}
summary.lm(model.1)
```
Model.1 show that the intercept 4.095 and coefficient 0.055 of ARM are both of these significantly different from 0.   

#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.1, targtPoint, interval = 'prediction')
print(predictInt)
```
This reflects ARM=88, GRIP=94 the predicted SIMS score is 0.71 The 95% confidence interval for that score is SIMS between -1.73 and 3.19.

#### scatterplot with model fit

```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~GRIP, data=data)
abline(model.2)
```   

This scatter plot reflects simulated strength (SIMS) increases as Grip strength increased.   

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

.64 reflects a moderate positive correlation between SIMS and Grip strength.  

### Inferential  (Build model.2)
  
```{r}
summary.lm(model.2)
```

Model.2 show that the intercept 4.81 and coefficient 0.045 of GRIP are both of these significantly different from 0.  

#### predict model.2 at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.2, targtPoint, interval = 'prediction')
print(predictInt)
```
This reflects ARM=88, GRIP=94 the predicted SIMS score is -0.54 The 95% confidence interval the score is SIMS between -3.10 and 2.04

#### now add the model fit to our plot for model.2
  
## Model 3 SIM~ARM+GRIP

```{r}
model.3 = lm(SIMS~ARM+GRIP, data=data)
summary(model.3)
```

Model.3 show that the intercept 5.43 and coefficient 0.037 of ARM and 0.24 of GRIP. The P Value for both is lower than 0.05.

### Numerical results (cor)

```{r}
cor(data)
```
SIMS correlates GRIP and ARM with these values

### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  
```{r}
predict(model.3, targtPoint, interval='prediction')
```
This reflects ARM=88, GRIP=94 the predicted SIMS score is -0.54 The 95% confidence interval the score is SIMS between -3.10 and 2.04

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova_results = anova(model.1,model.3)
print(anova_results)
```
Model 2 is much better than model 1 becuase the p value in comparison is less than 0.05


```{r}
anova_results = anova(model.2,model.3)
print(anova_results)
```
Model 3 is much better than model 1 because the p value in comparison is less than 0.05